CDSR Human Data/Modelling Paper

### 2013-09-12 scenarios/cdsr/trunk/papers/ACS2013/main.tex

\section{Discussion}

>>>>

\section{Discussion}
Cognitive systems do not face problems in isolation.  Context, including its goals, objects in the environment, and other agents, impact how information is processed and how actions are undertaken.  In this paper, we presented a human study to develop requirements for reasoning about context dependent spatial regions for cognitive systems.  We found that (1) people can communicate with CDSRs, although their ability to do so decreases when situations become ambiguous, and (2) varying the location and types of the objects and agents in an environment resulted predicted changes in the location, size, and shape of the spatial region.  We outline requirements for a cognitive systems solution and discuss limitations in current approaches from cognitive systems and robotics.  Solutions to this problem will significantly improve the interaction between people and intelligent systems in human environments with applications to domestic robots, security, and activity recognition.
